Learning to Group and Order AMR Semantics for General Purpose Discourse Planning

### 2015-12-10 paper/paper.tex
added table header

\begin{table}
\centering
\label{tab:order_features}
\begin{tabular}{|r|c|c|}
\hline
Feature & \\ \hline\hline
Pairwise Jaccard & Jaccard similarity of the AMR graphs for sentences $s_i,s_{i+1}$ \\ \hline
Two-apart Jaccard & Jaccard similarity of the AMR graphs for sentences $s_i,s_{i+2}$ \\ \hline
Pairwise node Jaccard & Jaccard similarity of just the vertex sets for sentences $s_i,s_{i+1}$ \\ \hline
Combined Jaccard & Jaccard similarity between the paragraph AMR and $s_i \cup
s_{i+1}$ \\ \hline
\end{tabular}
\caption{Description of features used by Subgraph Ordering Classifier}
\end{table}

>>>>

\begin{table}
\centering
\label{tab:order_features}
\begin{tabular}{|r|c|c|}
\hline
Feature & Description \\ \hline\hline
Pairwise Jaccard & Jaccard similarity of the AMR graphs for sentences $s_i,s_{i+1}$ \\ \hline
Two-apart Jaccard & Jaccard similarity of the AMR graphs for sentences $s_i,s_{i+2}$ \\ \hline
Pairwise node Jaccard & Jaccard similarity of just the vertex sets for sentences $s_i,s_{i+1}$ \\ \hline
Combined Jaccard & Jaccard similarity between the paragraph AMR and $s_i \cup
s_{i+1}$ \\ \hline
\end{tabular}
\caption{Description of features used by Subgraph Ordering Classifier}
\end{table}
